Convergent Evolution During Local Adaptation to Patchy Landscapes

### 2015-08-27 patchy-selection-paper.tex
.

\DeclareMathOperator{\var}{Var}
\DeclareMathOperator{\Exp}{Exp}
\DeclareMathOperator{\sn}{sn}
\renewcommand{\P}{\mathbb{P}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\calE}{\mathcal{E}}
\newcommand{\calC}{\mathcal{C}}
\newcommand{\dconv}{\xrightarrow{d}}
\newcommand{\deq}{\stackrel{\scriptscriptstyle{d}}{=}}
\newcommand{\given}{\,\vert\,}

@@

>>>>

\DeclareMathOperator{\var}{Var}
\DeclareMathOperator{\Exp}{Exp}
\DeclareMathOperator{\sn}{sn}
\DeclareMathOperator{\erf}{erf}
\renewcommand{\P}{\mathbb{P}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\calE}{\mathcal{E}}
\newcommand{\calC}{\mathcal{C}}
\newcommand{\dconv}{\xrightarrow{d}}
\newcommand{\deq}{\stackrel{\scriptscriptstyle{d}}{=}}
\newcommand{\given}{\,\vert\,}

@@

The remaining term is $q(S)$, the integral of equation \eqref{eqn:eqfreq} over the patch.
Suppose the new patch has width $w$, and is at distance $x$ from the original patch.
If the new patch is small ($w \ll \sigma/\sqrt{2s_m}$), 
then $q(S)$ is approximately $q(x)$ multiplied by the area of the new patch.
If the new patch is a long rectangle with width $u$ with long axis pointed towards the old patch,
$q(S)$ is approximately $u C \sqrt{\sigma/\sqrt{2s_m}} \erf(\sqrt{x\sqrt{2s_m}/\sigma})$,
where $\erf()$ is the error function.
